KidsAIR: manuscript tables/figures

### 2020-09-23 manuscript_tables_figures.Rmd
New RMD for main analysis

@@

ak_ids <- read_rds(paste0(file_path, "Output/ak_ids_linked.rds"))
nn_ids <- read_rds(paste0(file_path, "Output/nn_ids_linked.rds"))
wmt_ids <- read_rds(paste0(file_path, "Output/wmt_ids_linked.rds"))

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  filter(!is.na(treatment)) %>% 
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>%
  count(area, winter_id, treatment) %>% 
  filter(winter_id != 2)
```

>>>>

treatments_masked <- read_csv(paste0(file_path, "Input/KidsAIRrnd_masked.csv"), na = "NULL") %>% 
  mutate(home = gsub(" ", "", x = home),
         home = gsub("_", "", x = home))

@@

ak_ids <- read_rds(paste0(file_path, "Output/ak_ids_linked.rds")) %>% 
  mutate(home = gsub(" ", "", x = home),
         home = gsub("_", "", x = home))
nn_ids <- read_rds(paste0(file_path, "Output/nn_ids_linked.rds")) %>% 
  mutate(home = gsub(" ", "", x = home),
         home = gsub("_", "", x = home))
wmt_ids <- read_rds(paste0(file_path, "Output/wmt_ids_linked.rds")) %>% 
  mutate(home = gsub(" ", "", x = home),
         home = gsub("_", "", x = home))

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  filter(!is.na(treatment)) %>% 
  ### WMA222 and WMA 233 had a treatment but no kids - not counting in flow chart
  filter(home != "WMA222" & home != "WMA233") %>%
  count(area, winter_id, treatment) %>% 
  filter(winter_id != 2)

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  select(-treatment) %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(home)) %>% 
  mutate(original = 1) %>% 
  right_join(treatments_masked, by = "home") %>% 
  filter(home != "WMA222" & home != "WMA233") %>%
  filter(original == 1)
```
